---
title: "R_Markdown"
author: "Peterchen"
date: "2019年5月10日"
output: html_document
---
### [Some Statistic Function]  
### [Predict model]  
+ [Linear model]  
+ [Linear model predict]  
+ [t-test]   
+ [Two Sample t-test]    
+ [F-test of the equality of two variances]  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Some Statistic Function    
### 平均數 `mean()`  
```{r mean}
iris$Sepal.Length
mean(iris$Sepal.Length)
```
### 變異數 `var()`  
```{r var}
var(iris$Sepal.Length)
```
### 標準差 `sd()`
```{r sd}
sqrt(var(iris$Sepal.Length))
sd(iris$Sepal.Length)
```
### 四分位距 `quantile()` 
```{r quantile}
quantile(iris$Sepal.Length)
```
# Predict model  
### Linear model   
```{r linear model}
require(graphics)
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))            #Ctl*10 Trt*10
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1) # omitting intercept

anova(lm.D9)
summary(lm.D90)

opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0))
plot(lm.D9, las = 1)      # Residuals, Fitted, ...
par(opar)
```
### Linear model predict  
```{r prediction of linear model}
x <- rnorm(15)
y <- x + rnorm(15)
predict(lm(y ~ x))
new <- data.frame(x = seq(-3, 3, 0.5))
predict(lm(y ~ x), new, se.fit = TRUE)
pred.w.plim <- predict(lm(y ~ x), new, interval = "prediction")
pred.w.clim <- predict(lm(y ~ x), new, interval = "confidence")
matplot(new$x, cbind(pred.w.clim, pred.w.plim[,-1]),
        lty = c(1,2,2,3,3), type = "l", ylab = "predicted y")
```  

### t-test  
預設為  
`t.test(x, y = NULL,alternative ="two.sided",mu = 0, paired = FALSE,var.equal = FALSE,conf.level = 0.95, ...)`  

>alternative= 
>
>>"two.sided"  
>>"less"  
>>"greater"  
```{r t test}  
daily.intake <- c(5260,5470,5640,6180,6390,6515,6805,7515,7515,8230,8770)
t.test(daily.intake,mu=7725)
```  

### Two Sample t-test  
```{r two_sample_t_test}
#install.packages("ISwR")
library(ISwR)
attach(energy)
energy

t.test(expend~stature)
t.test(expend~stature, var.equal=T)
```  
### F-test of the equality of two variances  
```{r F_test_of_the_equality_of_two_variances}
var.test(expend~stature) 
```




